---
title: "R Notebook"
output: html_notebook
---
```{r}
# remove all from memory -----
library(knitr)
library(rmarkdown)
library(tidyverse)
library(lubridate)
library(stringr)
# library(forcats)
library(modelr)
# library(broom)
library(pander)
library(readxl)
library(NLP)
library(tm)
library(rlist)
library(quantmod) # Financial library

rm(list=ls())

source("code_01_functions.R")
```

# get the stock data for the stocks that meet the rsi threshold
```{r}
symbols = c('AAPL','GOOG','EMAN')
dl2 <- f2_get_stock_data(symbols, days = 120)
head(dl2[[1]])

```

#' convert the stocks to a data frame, rename the columns, flatten and nest
```{r}
by_stock <- f5_flatten_and_nest_by_stock(dl2)

by_stock
```

```{r}
unnest(by_stock, data)
```

Keep only needed data columns and get rsi. filter out na's
```{r}
by_stock <- by_stock %>%
  mutate(data = map(data, get_rsi_thresholds)) 
unnest(by_stock, data)
```


```{r}
by_stock <- by_stock %>%
  mutate(model = map(data, f6_buy_sell_hold_model, buy = .3, sell = .8, buy_sell_percent = .2))

by_stock$model[[1]]
```

```{r}
unnest(by_stock, model) %>%
  ggplot(aes(x = date, y = hold.stock.roi) ) + geom_line() + 
  facet_wrap( ~stock)
```

```{r}
unnest(by_stock, model) %>%
  ggplot(aes(x = date, y = investing.total), color = "green") +  geom_line() + 
  geom_line(aes(y = cash.only.total), color = "blue") +
  geom_line(aes(y = hold.stock.total), color = "red") +
  facet_wrap(~stock )
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
