---
title: "d_dollars Notebook"
output: html_notebook
---

```{r load_librarys, message=FALSE, include=FALSE}
# remove all from memory -----
library(knitr)
library(rmarkdown)
library(tidyverse)
library(lubridate)
library(stringr)
# library(forcats)
library(modelr)
# library(broom)
library(pander)
library(readxl)
library(NLP)
library(tm)
library(rlist)
library(quantmod) # Financial library
library(treemap)

rm(list=ls())

source("code_01_functions.R")
source("code_00_functions.R")
```

### Create a data list of stocks
```{r get_list_of_stocks, echo=FALSE}

# symbols = c('AAPL','GOOG','EMAN')
  
# read in the stock list table
stocks <- read_csv(file = "./data/companylist.csv", 
               col_types = cols(
                                  Symbol    = col_character(),
                                  Name      = col_character(),
                                  LastSale  = col_number(),
                                  MarketCap = col_number(),
                                  `ADR TSO` = col_skip(),
                                  IPOyear   = col_skip(),
                                  Sector    = col_character(),
                                  Industry  = col_character(),
                                  `Summary Quote` = col_skip()),
               trim_ws = TRUE, col_names = TRUE)

# normalize the variable names
colnames(stocks) <- normalize_variable_names(stocks)

sectors <- stocks %>%
  group_by(sector) 

stocks %>%
  group_by(sector) %>%
  summarise(stocks_in_sector = n_distinct(symbol)) %>%
  arrange(desc(stocks_in_sector)) 

sectors %>% summarize(sectors_in_industry = n_distinct(industry))

energy <- stocks %>%
  filter(sector == "Energy") %>%
  arrange(industry, symbol) %>%
  select(industry, symbol, name) 

energy
  
symbols <- energy$symbol
```
#### We will focus on the 'Energy' sector.
```{r, echo=FALSE, fig.width=8}
stocks %>%
  arrange(desc(lastsale)) %>%
  # head(n = 70) %>%
  treemap(index = c("sector", "industry"), vSize = "marketcap", 
          # type="categorical", 
          vColor = "sector", title = "Top Industries & Sectors by Market Cap", algorithm = "pivotSize" )

stocks %>%
    filter(sector == "Energy") %>%
    arrange(desc(lastsale)) %>%
    head(n = 70)  %>%
    mutate(lastsale = as.numeric(lastsale)) %>%
    treemap(index = c("industry", "symbol"), vSize = "lastsale",  type = "index",
            title = "Top Energy Stocks by Last Sale Price")

stocks %>%
    filter(sector == "Energy") %>%
    arrange(desc(lastsale)) %>%
    head(n = 70)  %>%
    mutate(lastsale = as.numeric(lastsale)) %>%
    treemap(index = c("industry", "symbol"), vSize = "marketcap",  type = "index",
            title = "Top Energy Stocks by Market Cap")

```

### Get the stock data for the stocks that meet the rsi threshold
```{r f2_get_stock_data, echo=FALSE, warning=FALSE}
#'### ------------------------------------------------------------------------
# Get the stock data for the stocks that meet the rsi threshold
f2_get_stock_data <- function(symbols = c('AAPL','GOOG','EMAN' ), 
                              from, to =  today()){
  
  
  # returns a data list with containing the data from somes stocks of interest
  dl <- list()

  # uncomment symbols to test the function from within
  # symbols = c('AAPL','GOOG','EMAN')

   for(i in 1:length(symbols)) {
     
     symbols[i] -> symbol
     
     # specify the "from" date to desired start date
     tryit <- try(getSymbols(symbol, 
                             from        = from, 
                             to          = to,
                             src         = 'yahoo', 
                             auto.assign = FALSE))
     
     if(inherits(tryit, "try-error")){
       i <- i + 1} 
     
     else {
       # Add stock data to list
       dl[[i]] <- tryit 
       attr(dl[[i]], 'symbol') <- symbol
       attr
       rm(symbol)}
   }
  
  return(dl)
}

# stocks_data <- f2_get_stock_data(symbols = energy$symbol, from = mdy("1-1-2010"), to = mdy("1-1-2012") )

head(stocks_data[[1]])

# write_csv(x = stocks_data, path = "./report/stocks_data.csv")
```

```{r nest_stocks_data, echo=FALSE}
### ------------------------------------------------------------------------
#' convert the stocks to a data frame, rename the columns, flatten and nest
f5_flatten_and_nest_by_stock <- function(dl2){
  dl <- dl2
  
  for(i in 1:length(dl)) {
    # i = 1
    
    # get the stock name
    stock_name <- names(dl[[i]]) %>%
      str_split( pattern = "\\.") %>% 
      unlist() %>%
      first()
    
    # convert each xts object in the list to a dataframe
    dl[[i]] <- as.data.frame(dl[[i]])
    
    # rename the columns for each dataframe
    names(dl[[i]])
    
    colnames(dl[[i]]) <- c("open", "high", "low", "close", "volume", 
                           "adjusted")
    
    # take the dates that are in the row names and make them a column in the
    # dataframe. then add the stock name
    dl[[i]] <- dl[[i]] %>%
      mutate(date  = ymd(row.names(.))) %>%
      mutate(stock = stock_name)
  }

  # flatten the list of data frames into one dataframe
  dl_flat <- list.rbind(dl)

  dl_flat <- na.omit(dl_flat)
  head(dl_flat)
  
  # nest by each stock
  dl_nested <- dl_flat %>%
    group_by(stock) %>%
    nest()

  # return(dl_flat)
  return(dl_nested)
}

by_stock <- f5_flatten_and_nest_by_stock(stocks_data)

by_stock
unnest(by_stock, data)
```

```{r get_rsi_thresholds, echo=FALSE}
### ------------------------------------------------------------------------
#' keep only needed data columns and get rsi. filter out na's
get_rsi_thresholds <- function(df, periods = 14){
  # periods = 14
  
  # keep only needed columns
  # df <- select(df, stock, close, date)
  df <- select(df,  close, date)
  
  # calculate the rsi
  rsi <- RSI(price = df$close, n = periods)
  
  # round to fewer signifigant digits
  rsi <- round(rsi, digits = 1)
  
  # turn the ve into a dataframe
  data <- data.frame(df, rsi)
  
  # omit the first days that have no rsi threshold
  data <- na.omit(data)
  
  return(data)
}

# Keep only needed data columns and get rsi. filter out na's
by_stock <- by_stock %>%
  mutate(data = map(data, get_rsi_thresholds, periods = 15)) 

unnest(by_stock, data)
```

```{r run_scenario}
# Run a scenario given arbitrary buy, sell & percent arguments
by_stock <- by_stock %>%
  mutate(model = map(data, f6_buy_sell_hold_model, buy = 25, sell = 80, 
                     buy_sell_percent = .2))

by_stock$model[[2]]
```

# Plot the 'Return on Investment' (roi) for the scenario
```{r scenario_plot_roi, message=FALSE, warning=FALSE}

unnest(by_stock, model) %>%
  ggplot(aes(x = date, y = hold.stock.roi) ) + 
  geom_line(color = "red") + 
  geom_line(aes(y = investing.roi), color = "green") +
  geom_hline(mapping = NULL,  yintercept = 0, color = "blue") +
  theme(legend.position = "right") +
  facet_grid(stock ~.) + ylab("roi") + 
  ggtitle( "red = hold_stock, green = investing, blue = cash_only")

```

# Plot total cash value for the scenario
```{r scenario_plot_total_cash}
unnest(by_stock, model) %>%
  ggplot(aes(x = date, y = investing.total)) +  
  geom_line( color = "green") + 
  geom_line(aes(y = cash.only.total),  color = "blue") +
  geom_line(aes(y = hold.stock.total), color = "red") +
  facet_grid(stock ~.) + ylab("total cash + stock in $")  + 
  ggtitle("blue = hold_cash, red = hold_stock, green = investing")
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
